\section{Short Baseline Accelerator Neutrinos}
\label{sec:AcceleratorSB}

(References to be added.) 

Accelerator decay-in-flight (DIF) neutrino beams provide an excellent opportunity for near-term, cost-effective neutrino experiments pursuing a variety of exciting physics and detector development goals.  The US is home to two existing neutrino beams, both located at Fermilab.  The Booster neutrino beam (BNB) has the significant advantage of being at shallow depth and parallel to the ground, enabling the deployment of multiple detectors at different baselines for relatively modest construction costs.  Improvements to the performance of the BNB are currently under consideration and would significantly strengthen all experiments that utilize this beam.  Preliminary studies indicate that a significant flux increase is feasible by fitting a second horn in the existing beam facility, although a detailed schedule and cost estimate needs to be prepared as recently requested by the Fermilab Physics Advisory Committee (PAC). New experiments on the Main Injector neutrino beam (NuMI) are also possible, but are limited by existing space in the underground near detector cavern.

A major element of the intermediate neutrino program will be the Short-Baseline Neutrino (SBN) program of three liquid argon detectors along the BNB.  The SBN program can resolve a class of experimental anomalies in neutrino physics and perform the most sensitive search to date for sterile neutrinos at the eV mass-scale through both appearance and disappearance oscillation channels. Additional physics includes the study of neutrino-argon cross sections with millions of interactions using the neutrino fluxes of the BNB (on-axis) and NuMI (off-axis) beams.  This program brings together an international team of scientists and engineers to advance the LAr-TPC technology for neutrino physics while utilizing its capabilities to explore one of the exciting open questions in neutrino physics today.  The SBN program was awarded stage-1 approval at Fermilab in February 2015.   Preparation of the three detectors is proceeding rapidly in order to match a tight time schedule that anticipates first data in 2018.  MicroBooNE is now installed on the BNB and  ready for commissioning, ICARUS is being refurbished at CERN in preparation for operations at shallow depth, and detailed designs are being developed for the near detector, LAr1-ND.

The Accelerator Neutrino Neutron Interaction Experiment (ANNIE) is another proposal to utilize the on-axis flux of the Booster neutrino beam.  ANNIE is a gadolinium doped water detector instrumented with advanced photodetectors that will measure neutron production in GeV-scale neutrino interactions, something presently not well understood and that represents a limiting factor in proton decay and supernova neutrino measurements in large water detectors.  ANNIE also presents an opportunity to demonstrate new Large Area Picosecond Photodetector (LAPPD) technology, now being commercialized through the DOE STTR program, in the context of a neutrino detector. ANNIE was awarded Stage-1 approval following the January meeting of the Fermilab PAC.

%ANNIE also presents an opportunity to demonstrate a novel new light collection technology in a neutrino detector, the Large Area Picosecond Photon Detectors (LAPPDs), now being developed.  ANNIE was also awarded Stage-1 approval following the January meeting of the Fermilab PAC.              

The CAPTAIN detector, a 5 ton LAr-TPC built at Los Alamos National Laboratory, anticipates running in both the BNB and NuMI neutrino beams.  By positioning the detector far off-axis at the BNB, CAPTAIN can study low energy neutrino interactions (10s of MeV) to better understand neutrino interactions in the energy range of supernova neutrinos that may be observed in future large LAr detectors.  The CAPTAIN-MINERvA experiment involves positioning the CAPTAIN detector in front of the existing MINERvA detector in the NuMI near detector hall to make precision measurements of neutrino-argon cross sections in the multi-GeV energy range.      

%The nuPRISM detector represents a novel approach to substantially reducing the impact of neutrino cross section model uncertainties in long-baseline oscillation experiments and has been proposed as part of the near detector complex at J-PARC in Japan.  By sampling the neutrino fluxes at angles from 0-4 degrees off-axis, representing different ranges of neutrino energy, nuPRISM can untangle the complicated energy-dependent effects of neutrino-nucleus interactions, including scattering off multiple correlated nucleon initial states.  nuPRISM also has sensitivity to sterile neutrino oscillations by sampling the beam at the same $L$ but different $E_{\nu}$ ranges.    

The NuPRISM detector represents a novel approach to substantially reducing the impact of neutrino cross section model uncertainties in long-baseline oscillation experiments, and has been proposed as part of the near detector complex at J-PARC in Japan. By sampling the neutrino beam at angles from 1-4 degrees off-axis, representing different ranges of neutrino energy, NuPRISM can map out the relationship between neutrino energy and the observed lepton kinematics. NuPRISM, in combination with the existing T2K near detector, also has sensitivity to sterile neutrino oscillations by sampling the beam at the same $L$ but different $E_{\nu}$ ranges. Finally, NuPRISM can construct mono-energetic beams to make unique neutrino cross section measurements, such as the first ever neutral current cross sections as a function of neutrino energy, and the separation of traditional CCQE events from interactions involving several nucleons.

Accelerator neutrino beam facilities and precision neutrino detectors present another exciting opportunity for the interim physics program.  By running in a 'beam-dump' mode (steering the proton beam off the target and into the beamline absorber), searches can be performed for dark sector particle production with reduced neutrino backgrounds.  The MiniBooNE experiment has recently collected data in this mode and is currently analyzing the results.  The LAr detectors of the SBN program present an opportunity to perform similar searches in the future with enhanced sensitivity.       
The need to understand the physics being pursued with these short-baseline accelerator beam experiments (anomalies, sterile neutrinos, neutron production, neutrino-nucleus cross sections) and the importance of developing detector technologies for the future neutrino program motivate an aggressive time scale for each of these experiments, making them ideal for an interim neutrino program on the road to the next generation US long-baseline experiment.  
