\subsection{Neutrino Detector R\&D}
\label{sec:RandD}

\subsubsection{Water and Liquid Scintillator}

Development of new scintillator materials and doping agents has proven
critical to the advancement of neutrino detector design. Further
development of these materials is a critical step for future
experiments; supporting this effort should be a high priority in the
intermediate program. This program includes target development and
characterization, including: light yield and timing measurements at
low and high energy, energy nonlinearity, and attenuation
measurements.

The newly-developed water based liquid scintillator (WbLS) could
enable a massive detector with a broad physics program at relatively
low cost. A particularly nice feature is the potential to separate
fast, directional Cherenkov light from the slower yet far more
abundant isotropic scintillation light. Should this be achieved, this
would enable astonishing advances in signal identification and
background rejection capabilities via particle identification,
resulting in vast improvements in physics reach. This potential
capability should be explored via both optimization of the WbLS target
--- by modifying the LS fraction and thus relative magnitudes of the
Cherenkov and scintillation components, by use of various additives to
delay the scintillation light, or wavelength shifters to minimize
absorption/reemission of Cherenkov light --- and alternate photon
detection methods. The ability to reconstruct event energy and
direction in (Wb)LS needs to be demonstrated both theoretically (in
simulation) and in practice (in small scale experiments).

Large water Cherenkov and (water-based) scintillator detectors require
very high purity target liquids.  Purification techniques for water
are well understood in industry and need no R\&D, but further
development is required for (Wb)LS purification. At the same time, a
program to determine compatibility of construction materials with
(Wb)LS must exist for future detectors.

Isotope loading in traditional liquid scintillator, Gadolinium doping
in water detectors, and the potential to load metallic isotopes in
WbLS broaden the potential physics program and significantly enhance
the sensitivity of future experiments. Techniques to load isotope
while maintaining the optical purity of the target should continue to
be developed.

A driving cost and critical performance factor in large-scale water or
scintillator detectors is the photomultiplier tubes. R\&D to produce
low cost, large area, ultra-fast photon detectors is important for the
neutrino community. Correspondingly fast, high precision readout will
be critical to take advantage of developments in photon detector
technology.

Water-based detectors (including WbLS) have the advantage of a low
cost detector medium allowing very large-scale experiments. Future
experiments will be limited by the cost and excavation techniques for
the cavern needed to house the experiments. R\&D to find lower-cost
construction methods, including PMT deployment and readout techniques,
can facilitate next-generation neutrino detectors.

Several projects are underway that can address these topics. These
range from bench-top scale development and characterization of
newly-developed WbLS and LS for next-generation large-scale detectors,
primarily at BNL but also at U. Chicago, U. Penn, LBNL, Iowa State,
and MIT, to full-scale projects such as EGADS (Gd loading), ANNIE
(fast timing), WATCHMAN phase II (WbLS deployment, fast timing), SNO+
(Te loading), and CHIPS (large-scale construction). This collaborative
effort is supported by DOE-HEP, DOE-NP, NSF and LDRD. Ultimately such
projects will inform the design of a massive future detector such as
the proposed \textsc{Theia} experiment.


\subsubsection{Liquid Argon}

Several ongoing and proposed experimental efforts will provide R\&D
that will substantially improve understanding of LArTPC performance or
potentially expand the capabilities of the ELBNF experiment. Test beam
measurements are especially important as they provide critical data
for improving the detector model and understanding of systematic
uncertainties.  The majority of these experiments will use the test
beam facilities at FNAL or CERN or the neutrino beams at FNAL. Support
for these efforts can be a combination of R\&D funding at FNAL, SBN or
ELBNF project funding, funding from an intermediate neutrino program
or other agency or laboratory funding.  Careful evaluation and
prioritization of these experiments by the FNAL PAC including an
evaluation of impact of R\&D by these experiments is expected, and
should provide important guidance to the selection process. However,
the substantially larger funding available to the FNAL projects should
also be taken into account. Only one experiment that will provide
critical R\&D needed for the ELBNF program is outside the FNAL
program: the neutron cross section measurements proposed by the
CAPTAIN experiment are necessary to understand the detector response
and energy resolution.

The following factors should be taken into account when evaluating the
impact different experiments could have on the long range program:
\begin{itemize}

\item A comprehensive test beam program must be performed to
  characterize present and future LArTPCs. This is necessary to
  calibrate the detector response of existing and future LAr detectors
  and to verify systematic error estimates. This program should
  include electromagnetic and hadronic showers measurements, neutron
  cross section measurements, and energy deposition measurements with
  different charged particle beams at appropriate
  energies. Experiments which could contribute to this are LArIAT,
  CAPTAIN, and the CERN neutrino platform experiments.

\item R\&D on the generation and breakdown of high voltage will reduce
  the risk to future LAr detectors and could lead to more monolithic
  and lower cost detector designs based on longer drifts. The causes
  of HV breakdown in LAr are not well understood. If the process for
  HV discharge in LAr is better understood then detectors could be
  designed for higher voltages (if the electron lifetime is
  sufficiently large). This could lead to larger, cheaper detectors
  and could enable dual-phase style detectors. R\&D on LAr
  feedthroughs above 100~kV is needed as manufacture of LAr feedthrus
  for voltages above 100 kV has only been achieved successfully by a
  small number of groups.

\item The processes for contamination generation and transport inside
  large liquid argon detectors are not well understood. Better
  modeling of the sources and migration of contaminants in large
  cryogenics systems will aid future detector design.

\item R\&D that improves the understanding of the generation and
  propagation of both light and charge in large LArTPCs will improve
  the detector model for ELBNF.
 
\item Present photon detector designs capture a very small fraction of
  the scintillation light generated in large LArTPCs. Detectors with
  better light collection efficiency should be developed.

\item Development of cold electronics for LArTPCs is
  critical. Advanced designs for cold preamps and ADCs exist but a
  control chip is only in early stages of development. Development of
  electronics to read out large arrays of SiPMs is necessary.

\end{itemize}




