\section{Introduction}
\label{sec:Introduction}


The US neutrino community gathered at the Workshop on the Intermediate
Neutrino Program (WINP) at Brookhaven National Laboratory February
4--6, 2015 to explore opportunities in neutrino physics over the next
five to ten years.  The US High Energy Physics community is now
launched on the path defined by the 2014 P5 report.  The US neutrino
community is primarily motivated by two of the five intertwined P5
science Drivers for the field, \textit{``Pursue the physics associated
  with neutrino mass''} and \textit{``Explore the unknown: new
  particles, interactions, and physical principles''}.

Underlying these Drivers is the fact that in spite of tremendous
recent progress in understanding neutrinos, we still lack a complete
picture for the physical behavior and structure of the
neutrino sector. There are many more questions yet to be answered:
What is the neutrino mass ordering? Do neutrinos exhibit the same
matter/antimatter symmetry seen in the charged leptons and quarks
(Dirac fermions) or do they have a completely different structure
(e.g., Majorana fermions)?  Do they violate CP symmetry?  What is the
absolute mass scale of the neutrino sector and is it consistent with
that implied from limits obtained by cosmological observation? Are
experimental hints that there may be additional sterile flavors of
neutrinos valid?  How can we understand neutrino interactions with
nuclei?  Are there non-standard interactions of neutrinos representing
beyond-the-Standard Model physics? 

There are furthermore outstanding questions which can be answered
using neutrinos as a probe, such as: What is the detailed mechanism
behind stellar-collapse supernovae, and what physics can we learn from
a supernova neutrino burst? Is the diffuse flux of neutrinos from past
supernovae consistent with expectations from cosmology?  Where do
ultra high energy neutrinos come from?  What fraction of the Earth's
radiated heat comes from radioactivity?  What fraction of the Sun's
energy comes from the CNO cycle?  What fission isotopes are the main
producers of neutrinos and decay heat in a nuclear reactor core?

In accordance with one specific P5 recommendation, a large international
collaboration (Experimental program at the Long-Baseline Neutrino
Facility, ELBNF) has been formed to perform a long-baseline neutrino
oscillation experiment with an underground liquid argon time
projection chamber and a new neutrino beam from
Fermilab.  The main physics goals of ELBNF are to address some of the
outstanding neutrino questions, by measuring the value of
the CP-violating parameter $\delta$ and providing a definitive
determination of the mass hierarchy, as well as to search for baryon
number violation and record a burst of core-collapse supernova
neutrinos.  The US community is also engaged in development of a
short-baseline neutrino (SBN) program hosted at at Fermilab, to operate
coherently with the long-baseline program in order to address some of the 
short-baseline neutrino anomalies and support R\&D towards ELBNF. 
These activities are consistent with P5 recommendations.

The Fermilab long-baseline effort is exciting and compelling, but
is a long-term effort.  Physics results and technical development in
the short term (this decade) are essential for health of the field,
for motivating young scientists and for sustaining innovation.  The
long-baseline oscillation program addresses some of the most critical
questions in particle physics --- yet other physics questions
associated with neutrinos, including the ones listed above, deserve
attention as well.  Some of these are best addressed with smaller,
lower-cost, dedicated experiments which can be completed
on a shorter time scale than ELBNF.  In addition, some issues will
need large, advanced-technology detectors which require
significant R\&D for their realization.

The P5 report states:
\textit{Some of the biggest scientific questions driving the field can only be
addressed by large and mid-scale experiments. However, small-scale
experiments can also address many of the questions related to the
Drivers. These experiments combine timely physics with opportunities
for a broad exposure to new experimental techniques, provide
leadership roles for young scientists, and allow for partnerships
among universities and national laboratories. In our budget exercises,
we main- tained a small projects portfolio to preserve budgetary space
for a number of these important small projects, whose costs are
typically less than \$20M. These projects individually are not large
enough to come under direct P5 review. Small investments in large,
multi-disciplinary projects, as well as early R\&D for some project
concepts, were also accounted for here.}\\
\textit{{Recommendation 4: Maintain a program of projects of all
  scales, from the largest international projects to mid- and
  small-scale projects.}}


WINP explored opportunities for the US neutrino community to pursue
physics in the next five to ten years, including projects of all
scales.  In addition to small- and mid-scale project ideas, WINP
considered (consistent with the P5 recommendation) contributions to
large offshore and multi-disciplinary projects, and to R\&D efforts
aimed towards future large experimental concepts.  Some of these ideas
and efforts are synergistic with the ELBNF and SBN efforts; others are
complementary.  Theory efforts related to the proposed long- and
short-term experimental programs were also discussed.

The workshop was organized into two sets of parallel working group
sessions, divided by physics topics and technology.  Physics working
groups covered topics on Sterile Neutrino, Neutrino Mixing, Neutrino
Interactions, Neutrino Properties and Astrophysical Neutrinos.
Technology sessions were organized into Theory, Short-Baseline
Accelerator Neutrinos, Reactor Neutrinos, Detector R\&D and Source,
Cyclotron and Meson Decay at Rest sessions.  Each working group
formulated a set of bullet points with key findings and
recommendations, which will be summarized in this report.

%\textit{Be explicit about the FOA here?  How much detail? Or does that make it
%  non-arXivable?   (May not be arXivable anyway)?

In addition to members of the particle and nuclear physics
communities, representatives from the agencies participated in the workshop.

A major area of discussion centered around a possible Department of Energy
Office of High Energy Physics Funding Opportunity
Announcement (FOA) relevant to neutrino physics over a five-year timescale.
Discussion sessions included community suggestions on physics topics and parameters for such a FOA.
The general outcome of this discussion was that the community believes that a
broader rather than a narrower scientific scope is important for any such FOA.  There was no clear
consensus on the appropriate fraction of available funds to be
allocated to R\&D efforts, but R\&D was felt to be important.  
Potential for publishable results ---
either physics, or key technical results that advance the field ---
within five years should be the most important criterion.  There was
also community support to enable proposals for theoretical effort.
These can be highly cost-effective and may strongly enhance the
success of experimental efforts.  
%Finally, there was consensus that the FOA would be most effective in enabling new experiments and ideas, and as such, efforts already approved under the existing Fermilab program should not be considered.
The community felt that a suite of new experiments should be
initiated, consistent with the P5 recommendation, to increase the
breadth of the intermediate program beyond SBN at FNAL. A general
sense emerged that some part of this new program should include
sterile neutrino searches complementary to SBN and that part of this
program should include some of the other exciting new initiatives
discussed.

Although much discussion focused on the potential HEP FOA, a broader
neutrino community beyond just those supported by DOE HEP was actively
engaged at the workshop, and it was clear that there are additional
opportunities for activities on an intermediate time scale that might
not fit within the FOA.  For example, another area of discussion was
the importance of determining the nature of the neutrino.  Whether
neutrinos are Majorana or Dirac is of fundamental importance to their
mass generation mechanism and to leptogenesis; the search for
neutrinoless double beta decay offers the most promising (and possibly
only plausible) avenue for addressing this question.  The community
recognizes the importance of the Nuclear Science Advisory Committee Neutrinoless Double
Beta Decay subcommittee's charge to determine a path for stewardship
of the next generation of ton-scale experiments.  In addition, many
other small-scale intermediate activities --- including R\&D, theory,
and contributions to a variety of international efforts --- are
supported by the National Science Foundation and the DOE Office of
Nuclear Physics.


% \textit{  Not necessarily to include:
% Josh's list, slightly edited... can modify based on some of
%   the other material}
% %The discovery of neutrino mass and mixing has led to a need for a diverse set of experiments to understand the fundamental nature and interactions of neutrinos.

% Topics of interest are:

% \begin{itemize}
% \item What are the values of the mixing parameters, mass differences, and CP-violating phase?

% \item What is the fundamental nature of the neutrino, and what are the values of parameters describing their properties?

% \item Are the anomalous appearance results of short-baseline accelerator experiments due to a new, sterile neutrino state?

% \item How do neutrinos interact with nuclei over a range of energies,
%   from MeV to multi-GeV scale?
% %Can we understand including resultant hadron multiplicities,
% %final-state interactions, multi-nucleon effects? 

% \item How can we optimize the physics output should a burst of neutrinos from a supernova be detected?

% \item What are the most interesting new technologies for detecting neutrinos, and what R\&D is necessary to develop them fully?

% \end{itemize}


%  This P5 wording could probably go in the sterile neutrino section

% Hints from short-baseline experiments suggest possible new
% non-interacting neutrino types or non-standard interactions of
% ordinary neutrinos. These anomalies can be addressed by proposed
% experiments with neutrinos from radioactive sources, pion
% decay-at-rest beams, pion and kaon decay-in-flight beams, muon-decay
% beams, or nuclear reactors. A judiciously selected subset of
% experiments can definitively address the sterile-neu- trino
% interpretation of the anomalies and potentially provide a platform for
% detector development and international coor- dination toward
% LBNF. These small-scale experiments are in addition to the small
% projects portfolio described above, and therefore appear separately in
% Table 1. The short-term short-base- line (SBL) science and detector
% development program and the long-term 
% LBNF program should be made as coherent as possible in an optimized neutrino program.
% Recommendation 15: Select and perform in the short term a set of small-scale short-baseline experiments that can conclusively address experimental hints of physics beyond the three-neutrino paradigm. Some of these experiments should use liquid argon to advance the technology and build the international community for LBNF at Fermilab.

