\pagebreak
\section{Reactor Neutrinos}
\label{sec:Reactor}

Reactor neutrinos have played a central role in the history and our
understanding of neutrinos.  From the first experimental observation
of the neutrino by Reines and Cowan at the Savannah reactor in the
1950's~\cite{Reines:1960pr} to the demonstration of neutrino
oscillations with KamLAND~\cite{Abe:2008aa} and the recent precision
measurement of the neutrino mixing angle
$\theta_{13}$~\cite{Abe:2012tg, An:2013zwz}, reactor neutrinos have
provided us with a unique tool for discovery for over five
decades. Reactor experiments have advanced our understanding of the
3-neutrino framework and enabled the most precise measurement of
neutrino mixing.

Emission of electron antineutrinos from reactors provides a
flavor-pure source of antineutrinos with energies up to $\sim$8~MeV. 
Reactor neutrinos are studied at distances as close as several
meters from the reactor core and detected up to hundreds of kilometers
from a nuclear power plant.  The abundant flux of antineutrinos from a
nuclear reactor allows experiments to probe for new physics such as
sterile neutrinos and neutrino magnetic moments, provide an
opportunity to observe coherent neutrino scattering, and make a
determination of the neutrino mass hierarchy. The detection and study
of reactor antineutrinos allows the monitoring and study of the power
and fuel composition of reactors and finds application in
non-proliferation and safeguards.

{\bf Physics Reach and Discovery Potential:}
Over the next decade neutrino experiments will make precision tests of
3-neutrino oscillations, aim to understand anomalous signatures in the
current suite of neutrino data, determine the mass hierarchy and
search for new CP violation. Reactor experiments will play a unique
and complementary role in this program and provide discovery potential
of new physics at modest costs. The observation of sterile neutrinos
or other new physics would be a paradigm shift and set the course of
particle physics for years to come.  The resolution of the neutrino
mass hierarchy will provide crucial input to determining the nature of
neutrinos.  Precision measurements of neutrino mixing parameters and
knowledge of the mass hierarchy will help maximize the physics reach
of long-baseline experiments and are fundamental to any extensions to
the Standard Model.

Measurements of the reactor neutrino flux and spectrum compared to
recent models of reactor antineutrino production have revealed
discrepancies in both the total measured reactor antineutrino flux as
well as the energy spectrum of neutrinos. The observed flux is found
to be $\sim$5--6\% low~\cite{Mention:2011rk, Zhang:2013ela} while the
recent $\theta_{13}$ experiments have revealed a distortion in the 4--6
MeV region of the spectrum.  The observed discrepancies may point to
new physics such as eV-scale sterile neutrinos and already indicate
that nuclear models in the predictions of the antineutrino flux from
reactors are incomplete.  Only a well-controlled measurement of the
antineutrino flux and spectrum at short-baselines can directly address
these questions. A search for antineutrino oscillations over
meter-long baselines probes the hypothesis of sterile neutrinos in the
appropriate mass region while a measurement of the flux and spectrum
can inform our understanding of antineutrino emission from reactors.
Over distances of some fifty kilometers the observed oscillated energy
spectrum provides a unique method for the determination of the mass
hierarchy along with precision measurements of neutrino mixing
parameters.

{\bf Reactors and Experimental Facilities:}
The US has access to several reactor facilities that are are
well-suited for short-baseline experiments at distances of
$\mathcal{O}$(10~m). The NIST, HFIR, and ATR reactors in the US
operate at 20--250~MW with highly enriched $^{235}$U, provide easy
access and technical support for a world-leading short-baseline
reactor neutrino experiment. Other compact, high-powered sources for
antineutrinos such as a naval reactor are being explored. Through
international collaboration the US also has an exciting opportunity to
participate in a medium baseline experiment overseas near the Taishang
and Yangjiang reactors in China.

% The reactor working group has identified the following opportunities for an intermediate neutrino program:

{\bf Small-Scale \& Short-Baseline -- Sterile Neutrinos and Reactor Spectrum:}
{\em A domestic short-baseline experiment designed to resolve the
reactor neutrino anomaly through oscillation and spectral measurements
has the potential to discover new physics in the next 3--5 years at
modest costs of \$3--4M.}  Proposed short-baseline reactor
disappearance experiments such as NuLAT~\cite{Lane:2015alq} and
PROSPECT~\cite{Ashenfelter:2013oaa} are complementary to the FNAL
short-baseline program focusing on appearance measurements, and will
answer both the question of short-baseline oscillation and our
understanding of the reactor antineutrino spectrum. The proposed
projects have deployed test detectors at NIST and HFIR, are ready to
proceed with full design and construction, and provide an opportunity
for world-leading, high-impact science at modest costs. In a
technically limited schedule data taking can begin in 2016 with first
physics results in 2017. Given US experience and available reactor
facilities, the US is in an excellent position to host and lead a
short-baseline reactor experiment. The experiments offer opportunities
for international collaboration with Canada, China, and Europe.
Several other efforts worldwide are at various stages of development
to search for short-baseline oscillations with reactor neutrinos. This
includes SOLID, STEREO, DANSS, and Neutrino-4. Experiments proposed in
the US aim to optimize physics sensitivity to both the reactor
spectrum and neutrino oscillations, proceed in a phased approach for a
cost effective physics search at limited cost, and provide
comprehensive systematic control through novel scintillator and
detector technologies, movable detectors, and extensive background
control. This comprehensive but phased approach will maximize the
discovery potential of the proposed US experiments, limit technical
risk, and provide flexibility to respond to future discoveries.
Timely execution is critical to guarantee the highest impact and
facilitate European participation in a US experiment.

{\bf Mid-Scale \& Medium-Baseline -- Mass Hierarchy and Oscillation Parameters:}
 {\em Medium-baseline experiments aim to determine the
neutrino mass hierarchy without matter effect and precisely measure
$\theta_{12}$, $\Delta m^2_{21}$, and $\Delta m^2_{32}$. over the next
7--10 years~\cite{Kettell:2013eos}. A US contribution can make a critical impact to one of
these overseas experiments.} The JUNO experiment in China and RENO-50
in Korea are designed to determine the neutrino mass hierarchy and
precisely measure oscillation parameters. In particular, the JUNO
experiment, hosted by China and with substantial European
contributions, embraces US participation. Leveraging the successful
US-China collaboration on Daya Bay, the US is well-positioned to make
an important contribution.  Near-term R\&D of a few \$M can help
define US scope focused on the calibration system with an eventual US
JUNO contribution of order \$20M over 5--8 years.  A reactor
experiment at medium baselines represents an excellent opportunity to
continue the long-standing US-China collaboration and ensures US
leadership in the determination of the mass hierarchy.

{\bf Synergies:} {\em Measurements of reactor neutrinos are also
relevant to nuclear physics and applied reactor safeguards. The
proposed experiments will continue the long-standing US expertise in
this area.} Short-baseline experiments provide opportunities for
detector R\&D into technologies such as novel scintillators and highly
segmented detectors. Large reactor antineutrino detectors offer
synergistic opportunities for geo-neutrino physics and
astrophysics. Many of the theoretical and experimental challenges are
common across these fields and reactor neutrino measurements have the
potential to uniquely inform these communities.
